A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2021-01-01 paper.tex
Add more info on the process of simulation

% Mention that the FHN eqns are nondimensional and so all quantities have dimension but not units, i.e., arbitrary scaling.

@@

@@

>>>>

% Mention that the FHN eqns are nondimensional and so all quantities have dimension but not units, i.e., arbitrary scaling.
We have used the FitzHugh-Nagumo equations for our model neurons; these equations are completely non-dimensional, meaning that their scaling is arbitrary.  As such, the constants, parameters, results, et cetera which we use have no units, and do not directly correspond to physical realities.

For a CPG model, each individual neuron has a set of parameters $\left\{α, γ, ε\right\}$ and each connection has a diffusion coefficient associated with it.  Additionally, it is easy to inject a current into a specific neuron, or to change a specific neuron's input requirements.

In short - each neuron in the CPG has two inputs from other neurons (the preceding neuron in the chain driving it, and the opposite neuron inhibiting it).

As such, there are five principal parameters per neuron: $α,\ γ,\ ε,\ D_\mathrm{desc},$ and $D_\mathrm{opp}$.  $D_\mathrm{desc}$ is the diffusion coefficient corresponding to the neuron directly before, and on the same side as, the ``current'' neuron.  Similarly, $D_\mathrm{opp}$ is the diffusion coefficient corresponding to the neuron on the opposite side of the nematode (dorsal or ventral).

These parameters are passed as an array to the function which solves the differential equation.  See ***Appendix A*** for parameter values which worked for us.

@@

Integration is done by a standard differential equation solver.  To use the SciPy/LSODA interface, the function must take as input three objects $u,\ p,\ t$.  Here, $u$ is the current state of the system (the values of $v$ and $w$ for each neuron), $p$ is the set of parameters for the system (in our case, all $α,\ γ,\ ε,\ D_\mathrm{desc},$ and $D_\mathrm{opp}$ per neuron) and $t$ is the time (which we do not use, since our DEs do not depend on time).

The function must then return an array $du$, containing the derivatives $dv$ and $dw$ from each neuron.  In our program, we have structured this so that systems are grouped together, that is, the array looks like $\left[dv_1, dw_1, dv_2, dw_2, ..., dv_i, dw_i\right]$.

The function we have written is structured such that the parameters and state are ``unpacked'' from input arrays first, and then the equations are solved.

@@

Essentially, the process is that
